### 2017-10-10 paper/incomeShocks-jde-r1.tex
Add highlights

>>>>

\section*{Highlights}

\begin{enumerate}
\item In Tanzania, likelihood of pregnancy and birth is lower after an income shock.
\item Contraception use, especially traditional, are higher after an income shock.
\item Postponement of fertility in response to shock appears to be conscious decision.
\item Traditional contraceptives have high efficacy after income shock. 
\end{enumerate}
